Current model cost effect

### 2020-09-24 src/current_model_effect.Rmd
critical x-axes label fix

```{r ,warning=FALSE}
#Get the a (y) and q (x) mappings for the optimised 6 and 12 month scenarios
x6 <- head(which(q.seq > tprs$q[which(tprs$E6 == min(tprs$E6))] ),1)
y6 <- head(which(adjustments > tprs$a6[which(tprs$E6 == min(tprs$E6))]),1)
x12 <- head(which(q.seq > tprs$q[which(tprs$E12 == min(tprs$E12))] ),1)
y12 <- head(which(adjustments > tprs$a12[which(tprs$E12 == min(tprs$E12))]),1)
#Plot them
colnames(E.long) <- c("adjustment", "q", "cost")
p <- ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
  geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, binwidth =  1) +
  scale_fill_gradientn(colours=c("blue", "red")) +
  labs(x="q% i.e. deferral rate", y=expression(a[tot]~i.e.~donation~interval~coefficient ))  + 
  theme_bw() +
  scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.2")) +
  scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
#Add numeric values of costs with optimised classifier probability cut-offs
p <- p + annotate("text" ,
                  x = x6 , 
                  y = y6 - 50,
                  label = paste0("6 mo: ", round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2),' (',round(deframe(p6.ci[4,2]),2)," - ",round(deframe(p6.ci[4,3]),2),') €'  ),
                  colour = "white")

>>>>

```{r ,warning=FALSE}
#Get the a (y) and q (x) mappings for the optimised 6 and 12 month scenarios
x6 <- head(which(q.seq > tprs$q[which(tprs$E6 == min(tprs$E6))] ),1)
y6 <- head(which(adjustments > tprs$a6[which(tprs$E6 == min(tprs$E6))]),1)
x12 <- head(which(q.seq > tprs$q[which(tprs$E12 == min(tprs$E12))] ),1)
y12 <- head(which(adjustments > tprs$a12[which(tprs$E12 == min(tprs$E12))]),1)
#Plot them
colnames(E.long) <- c("adjustment", "q", "cost")
p <- ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
  geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, binwidth =  1) +
  scale_fill_gradientn(colours=c("blue", "red")) +
  labs(x="q% i.e. rate of avoided deferrals", y=expression(a[tot]~i.e.~donation~interval~coefficient ))  + 
  theme_bw() +
  scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.2")) +
  scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
#Add numeric values of costs with optimised classifier probability cut-offs
p <- p + annotate("text" ,
                  x = x6 , 
                  y = y6 - 50,
                  label = paste0("6 mo: ", round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2),' (',round(deframe(p6.ci[4,2]),2)," - ",round(deframe(p6.ci[4,3]),2),') €'  ),
                  colour = "white")
